Using Sorghum as an outgroup to find syntenic regions in Maize: regenerating

### 2017-08-18 R/SubGenome Analysis.Rmd
Updated analysis to use the v4 SynMap data

---
title: 'Using Sorghum as an outgroup to find syntenic regions in Maize: regenerating
  subgenome assignments in maize'
params:
  fileParser: ../Perl/parseKsKnFile.pl
  goDataFile: ../Data/GO from maizecyc.tab
  log10_ks_cutoff: 0
  synMapOutputFile: 6807_8082.CDS-CDS.lastz.tdd10.cs0.filtered.dag.all.go_D20_g10_A5.aligncoords.gcoords.ks
  inputDataFile: ../Data/sorghum_v1_vs_maize_v1.tab
  subGenomeFile: ../Data/outfile_processed_byHand.tab

  # inputDataFile: ../Data/sorghum_v3.1_vs_maize_v4+rejected.tab
  # subGenomeFile: ../Data/outfile_processed_byHand.tab
output:
  html_document: default
  pdf_document: default
---

>>>>

---
title: 'Using Sorghum as an outgroup to find syntenic regions in Maize: regenerating
  subgenome assignments in maize'
params:
  fileParser: ../Perl/parseKsKnFile.pl
  goDataFile: ../Data/GO from maizecyc.tab
  log10_ks_cutoff: 0
  synMapOutputFile: 6807_8082.CDS-CDS.lastz.tdd10.cs0.filtered.dag.all.go_D20_g10_A5.aligncoords.gcoords.ks
  # inputDataFile: ../Data/sorghum_v1_vs_maize_v1.tab
  # subGenomeFile: ../Data/outfile_processed_byHand.tab

  inputDataFile: ../Data/sorghum_v3.1_vs_maize_v4+rejected.tab
  subGenomeFile: ../Data/outfile_processed_byHand.tab
output:
  html_document: default
  pdf_document: default
---
